On Secure Delegation of SampBQP with a Classical Client

### 2020-03-12 bqp-rewrite.tex
Work on blindness compiler intro

In this section we show a relatively simple way to create a blind and constant-round $\QPIP_0$ delegation protocol for $\BQP$. We create our protocol by running the constant-round $\QPIP_0$ protocol from \cite{FOCS:Mahadev18a} under $\QHE$ from \cite{mahadev_qfhe}.
This is possible due to additional properties of $\QHE$ that facilitates the use of a classical client. Its encryption can be performed classically.
Then, after the homomorphic evaluation, the server could homomorphically measure the ciphertexts and send the results for the classical client to decrypt.
In fact, this approach is powerful enough to give blindness to any $\QPIP_0$ protocol.

We start with a summarization of $\QHE$ and notations.
First, when there are many sets of $\QHE$ keys in play at the same time,
we use $\ctx{x}{i}$ to denote $x$ encrypted under $pk_i$.
Otherwise, we write $x'$ for a ciphertext corresponding to plaintext $x$.
Moreover, the encryption is done on a qubit-by-qubit basis,
so we can write $(x_1, x_2)'=(x_1', x_2')$.

@@

Finally, we show the blindness of $\Piblind$ through a standard hybrid argument:
\begin{theorem}
	$\Piblind$ is blind.
\end{theorem}
\begin{proof}
	Consider $T+1$ hybrids experiments, from $\Hyb_1$ to $\Hyb_{T+1}$.
	In $\Hyb_i$, we modify $(\Pblind, \Vblind(x))$ s.t.
	for all rounds associated with $\cV{t}$ where $t\geq i$, the verifier replaces the $\ctx{sk_{t-1}}{t}$ in its message with encryption of $0$.
	Then, for all $t$, $\Hyb_{t+1}$ is computationally indistinguishable from $\Hyb_t$ due to the CPA security of $\QHE$ under $pk_t$.
	Since computational indistinguishability is transitive \Ethan{really?}, $\Hyb_1$ is indistinguishable with $\Hyb_{T+1}$.
	Note that $\Hyb_{T+1}$ is precisely $\Piblind$, and $\Hyb_1$ is clearly blind. So $\Hyb_{T+1}$ is also blind.
\end{proof}

>>>>

In this section we show a relatively simple way to create a blind and constant-round delegation protocol with a classical client for $\BQP$, with negligible soundness and completeness errors.
We start with the protocol from \cite{parallelrep, alagic2019twomessage} which satisfies all our requirements except blindness.
Generally one can obtain blindness by running a protocol under homomorphic encryption. \Ethan{Maybe cite?} In our case, we have a classical client and a quantum server, so we choose the homomorphic encryption from \cite{mahadev_qfhe} that's compatible with this situation.

We start by summarizing additional properties of Mahadev's $\QHE$ that makes our construction possible.
First, when the plaintext is classical, the encryption can be performed classically.
Moreover, a quantum ciphertext can be measured homomorphically, in which case the measurement outcomes can then be decrypted classically.
Lastly, the encryption is done qubit-by-qubit, so one can split a ciphertext into registers as one would with the corresponding plaintext.

We now state our compiler that gives any $\QPIP_0$ protocol blindness.
For notation, when there are many sets of $\QHE$ keys in play at the same time,
we use $\ctx{x}{i}$ to denote $x$ encrypted under $pk_i$.
Otherwise, we write $x'$ for a ciphertext corresponding to plaintext $x$.
Moreover, the encryption is qubit-by-qubit,
so we can write $(x_1, x_2)'=(x_1', x_2')$.

@@

Finally, we show the blindness of $\Piblind$ through a standard hybrid argument:
\begin{theorem}
	$\Piblind$ is blind.
\end{theorem}
\begin{proof}
	Consider $T+1$ hybrids experiments, from $\Hyb_1$ to $\Hyb_{T+1}$.
	In $\Hyb_i$, we modify $(\Pblind, \Vblind(x))$ s.t.
	for all rounds associated with $\cV{t}$ where $t\geq i$, the verifier replaces the $\ctx{sk_{t-1}}{t}$ in its message with encryption of $0$.
	Then, for all $t$, $\Hyb_{t+1}$ is computationally indistinguishable from $\Hyb_t$ due to the CPA security of $\QHE$ under $pk_t$.
	Since computational indistinguishability is transitive \Ethan{Really? Definitely need to write down some inequalities here...}, $\Hyb_1$ is indistinguishable with $\Hyb_{T+1}$.
	Since $\Hyb_{T+1}$ is precisely $\Piblind$, and $\Hyb_1$ is clearly blind, we can conclude that $\Piblind$ is blind.
\end{proof}

### 2020-03-12 qpip.tex
Work on blindness compiler intro

Here we create a $\QPIP_1$ scheme for $\SampBQP$ by constructing a history XZ local Hamiltonian instance, and ask the prover to provide the ground state. In the case of decision problems, it would be a simple Chernoff bound as in \cite{kitaev2002classical}. A prover, honest or not, couldn't do better than sending $n$ identical copies of some state. The same reasoning does not work in our case, so we give the following construction instead.

@@

\begin{lemma}
	\label{ProtoGroundStateCheck}
	There is a $\QPIP_1$ protocol for \cref{AlgGroundStateCheck}. Furthermore, in this protocol, the verifier doesn't need to apply any gates, and only needs to apply $X$ and $Z$ measurements.
\end{lemma}
\begin{prf}
	The prover simply sends the input qubit-by-qubit for the verifier to measure. It is clear that any attacks on this scheme trivially maps onto an attack on the original scheme.
\end{prf}

>>>>

Here we create a $\QPIP_1$ scheme for $\SampBQP$ by constructing a history XZ local Hamiltonian instance, and ask the prover to provide the ground state.
\Ethan{Properly intro and point out the difference between BQP and SampBQP and the challenge here.}
In the case of decision problems, it would be a simple Chernoff bound as in \cite{kitaev2002classical}. A prover, honest or not, couldn't do better than sending $n$ identical copies of some state. The same reasoning does not work in our case, so we give the following construction instead.

@@

\def\GS{\mathsf{GS}}
\nc{\PiGS}{\ensuremath{\Pi_\GS}}
\nc{\VGS}{\ensuremath{V_\GS}}
\nc{\PGS}{\ensuremath{P_\GS}}
\nc{\PGSstar}{\ensuremath{P_\GS^*}}
\nc{\cVGS}[1]{\ensuremath{\cV_{\GS,#1}}}
\nc{\cPGS}[1]{\ensuremath{\cP_{\GS,#1}}}

\begin{lemma}
	\label{ProtoGroundStateCheck}
	There is a $\QPIP_1$ protocol $\PiGS$ for \cref{AlgGroundStateCheck}. Furthermore, in this protocol, the verifier doesn't need to apply any gates, and only needs to apply $X$ and $Z$ measurements.
\end{lemma}
\begin{prf}
	The prover simply sends the input qubit-by-qubit for the verifier to measure. It is clear that any attacks on this scheme trivially maps onto an attack on the original scheme.
\end{prf}

### 2020-03-12 qpip0.tex
Work on blindness compiler intro

\begin{definition}[computationally indistinguishable]
\hannote{move later}
Let  $D_1$ and $D_2$ be distributions over $n$-bit string.  We say $D_1$ and $D_2$  are $\eps$-Q-computationally indistinguishable if for all quantum circuit $A$ of size $\poly(n)$, $$\L\|\Pr[A({D_1})=1]-\Pr[A({D_2})=1]  \R\| \leq \eps,$$  where $A(D_1)$ means $A$ takes a sample from $D_1$ as part of its input. 
\end{definition}
%Let $O^{D_1}$ and $O^{D_2}$ be oracles giving samples from $D_1$ and $D_2$.

@@

>>>>

\begin{definition}[quantum computationally indistinguishable]
\hannote{move later}
Let  $D_1$ and $D_2$ be distributions over $n$-bit string.  We say $D_1$ and $D_2$  are $\eps$-Q-computationally indistinguishable if for all quantum circuit $A$ of size $\poly(n)$, $$\L\|\Pr[A({D_1})=1]-\Pr[A({D_2})=1]  \R\| \leq \eps,$$  where $A(D_1)$ means $A$ takes \emph{one} sample from $D_1$ as part of its input. We also denote this as 
$$ D_1 \approx_{q,\eps} D_2$$
\end{definition}
%Let $O^{D_1}$ and $O^{D_2}$ be oracles giving samples from $D_1$ and $D_2$.

\begin{rmk}
We extend the definition of computational distance to a subnormalized distribution  $D$  by assuming $A(D)=0$ when $A$ fail to draw a sample from $D$.
\end{rmk}

@@

\begin{lem}[triangle inequality for computational distance]
Let $D_1$, $D_2$ be two distributions such that $D_1=D_3+D_4$ and $D_2=D_5+D_6$, where $D_3$, $D_4$, $D_5$, and $D_6$ are subnormalized distributions.

If 
\begin{align}
    D_1 &\approx_{q,\eps} D_2 \\
    D_4 &\approx_{q,\eps'} D_6, 
\end{align}
then 
\begin{align}
    D_3 \approx_{q,\eps+\eps'} D_5
\end{align}
\end{lem}
\begin{proof}
